NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-06-26 paper/prediction.tex
finalize change in section 5
grammar fix

\subsection{Prediction View}
\label{sec:prediction}
For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradiction, and entailment).
%
In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment. The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
In the triangle, the distinctly colored background (grey, light grey, and light green) indicates the regions that correspond to different labels. The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs. A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictionView}
 \vspace{-5mm}
 \caption{
In the prediction view, the prediction is encoded as a point in the barycentric coordinate system of the triangle shown in (a).
 %
% The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
As illustrated in (b), the predicted label does not match the ground truth. Therefore, we apply a label reassignment operation, which triggers a model update.
% when press and drag the circle (prediction), the user is presented with the three option corresponds to the labels. The dotted line and arrow indicate the newly assigned label.
 }
  \vspace{-2mm}
\label{fig:predictionView}
\end{figure}

>>>>

\subsection{Prediction View}
\label{sec:prediction}
For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradiction, and entailment).
%
In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle.
Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction, or entailment. The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
In the triangle, the distinctly colored background (gray, light gray, and light green) indicates the regions that correspond to different labels. The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs. A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.
%\shusen{
The pattern of the perturbed pairs' prediction directly conveys the stability of the model for the given instance. 
Here, we should also take the length of the sentence into consideration as more nouns and verbs will likely lead to more varied perturbations.
%}

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{predictionView}
 \vspace{-5mm}
 \caption{
In the prediction view, the prediction is encoded as a point in the barycentric coordinate system of the triangle shown in (a).
 %
% The prediction result for the original sentence pair is represented by a larger yellow circle and the prediction of perturbed pairs are illustrated by smaller grey circles.
A density contour of the prediction is computed via kernel density estimation to emphasize the highly cluttered areas and distinguish the outliers.
As illustrated in (b), the predicted label does not match the ground truth. Therefore, we apply a label reassignment operation, which triggers a model update.
% when press and drag the circle (prediction), the user is presented with the three option corresponds to the labels. The dotted line and arrow indicate the newly assigned label.
}
\vspace{-2mm}
\label{fig:predictionView}
\end{figure}
